Reducing Linearizability of Priority Queues and More Data Structures to State Reachability

### 2017-06-29 co-regular-EPQ.tex
modify

When defining $\Gamma$-complete automata, we assume that every implementation $\mathcal{I}$ behaves correctly, i.e., as a FIFO queue, when only values with the same priority are observed. More precisely, we assume that for every execution $e\in\mathcal{I}$ and every priority $p\in\mathbb{P}$, the projection of $e$ to values with priority $p$ is linearizable (w.r.t. $\seqPQ$). This property can be checked separately using the techniques introduced for regular FIFO queues in~\cite{DBLP:conf/icalp/BouajjaniEEH15} (see Appendix~\ref{sec:appendix lemma and register automata for FIFO of single-priority executions} for more details). Note that this assumption excludes some obvious violations, such as a $\textit{rm}(a)$ operation happens before a $\textit{put}(a,p)$ operation, for some $p$.

>>>>

When defining $\Gamma$-complete automata, we assume that every implementation $\mathcal{I}$ behaves correctly, i.e., as a FIFO queue, when only values with the same priority are observed. More precisely, we assume that for every execution $e\in\mathcal{I}$ and every priority $p\in\mathbb{P}$, the projection of $e$ to values with priority $p$ is linearizable (w.r.t. $\seqPQ$). {\color {blue}This property can be checked separately using the techniques introduced for regular FIFO queues in~\cite{DBLP:conf/icalp/BouajjaniEEH15}} {\color {red}This property can be checked separately using register automata obtained from the finite automata in~\cite{DBLP:conf/icalp/BouajjaniEEH15} for FIFO queue} (see Appendix~\ref{sec:appendix lemma and register automata for FIFO of single-priority executions} for more details). Note that this assumption excludes some obvious violations, such as a $\textit{rm}(a)$ operation happens before a $\textit{put}(a,p)$ operation, for some $p$.
